On exponential sums arising from the classical doubling method

### 2025-03-21 paper.tex
Calvin update
Adding signed Jacobi sums

% Finite field macros
\newcommand{\FieldNorm}[2]{\mathrm{N}_{#1:#2}}
\newcommand{\aFieldNorm}{\mathrm{N}}
\newcommand{\finiteField}{\mathbb{F}}
\newcommand{\quadraticExtension}{\mathbb{E}}
\newcommand{\finiteFieldExtension}[1]{\finiteField_{#1}}
\newcommand{\quadraticFieldExtension}[1]{\quadraticExtension_{#1}}
\newcommand{\NormOneGroup}[1]{\finiteFieldExtension{#1}^{\aFieldNorm = 1}}
\newcommand{\algebraicClosure}[1]{\overline{#1}}
\newcommand{\Galois}{\operatorname{Gal}}
\newcommand{\Frobenius}{\operatorname{Fr}}
\newcommand{\restrictionOfScalars}[3]{\operatorname{Res}_{#1 \slash #2}{#3}}
\newcommand{\multiplcativeScheme}{\algebraicGroup{G}_m}
\newcommand{\affineLine}{\mathbb{A}^1}
\newcommand{\squareMatrix}{\operatorname{Mat}}
\newcommand{\Mat}[2]{\operatorname{Mat}_{#1 \times #2}}
\newcommand{\GaussSum}[2]{\mathcal{G}\left(#1, #2\right)}
\newcommand{\dblJacobiSum}[2]{\mathcal{J}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\GaussSumScalar}[2]{\mathrm{G}\left(#1, #2\right)}
\newcommand{\dblJacobiSumScalar}[2]{\mathrm{J}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblVirtualJacobiSumScalar}[2]{\mathrm{j}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblGammaFactor}[3]{\Gamma^{\mathrm{dbl}}\left(#1 \times #2, #3\right)}
\newcommand{\dblGammaFactorSpace}[4]{\Gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\dblLanglandsGammaFactorSpace}[4]{\gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\GaussSumCharacter}[3]{\tau\left(#1 \times #2, #3\right)}
\newcommand{\ladicnumbers}{\algebraicClosure{\mathbb{Q}_{\ell}}}
\newcommand{\IsometryGroup}{\mathrm{Isom}}
\newcommand{\lieAlgebra}{\mathfrak{g}}
\newcommand{\DeligneLusztigInduction}[2]{\mathrm{R}_{#1}^{#2}}
\newcommand{\algebraicGroup}[1]{\boldsymbol{\mathrm{#1}}}
\newcommand{\LusztigSeries}[2]{\mathcal{E}\left(#1, (#2)\right)}
\newcommand{\characteristicPolynomial}{\operatorname{CharPoly}}
\newcommand{\DualFrobeniusFixedPoints}[2][\Frobenius^{\ast}]{\algebraicGroup{#2}^{\ast #1}}
\newcommand{\FrobeniusFixedPoints}[2][\Frobenius]{\algebraicGroup{#2}^{#1}}
\newcommand{\CharacterLattice}[1]{X^{\ast}\left(#1\right)}
\newcommand{\CocharacterLattice}[1]{X_{\ast}\left(#1\right)}

@@

Consider the following assignment $\GL_k\left(\finiteField\right) \to \cComplex$
$$\Phi_{\chi}\left(g\right) = \begin{dcases}
	\chi\left(\det\left(\IdentityMatrix{k}-g\right)\right) & \text{if }\det\left(\IdentityMatrix{k}-g\right) \ne 0,\\
	0 & \text{otherwise.}
\end{dcases}$$
It is clear that $\Phi_{\chi}$ is a class function of $\GL_k\left(\finiteField\right)$.

Given an irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$, we consider the following \emph{doubling method Jacobi sum}:
$$\dblJacobiSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{g \in \GL_k\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \tau\left(g\right).$$
Then $\dblJacobiSum{\tau}{\chi}$ defines an element of $\Hom_{\GL_k\left(\finiteField\right)}\left(\tau, \tau\right)$. Therefore, by Schur's lemma there exists a complex number $\dblJacobiSumScalar{\tau}{\chi} \in \cComplex$ such that $$\dblJacobiSum{\tau}{\chi} = \dblJacobiSumScalar{\tau}{\chi} \cdot \idmap_\tau.$$

The goal of this section is to express $\dblJacobiSumScalar{\tau}{\chi}$ in terms of Kondo's Gauss sum.

\begin{proposition}\label{prop:doubling-for-gln-in-terms-of-kondo}
	We have the identity
	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
\end{proposition}
\begin{proof}
	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det\left(-h\right)\right).$$
	By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $X \in \GL_k\left(\finiteField\right)$. Thus	$$\Phi_{\chi}\left(g\right) = \frac{\chi\left(-1\right)^k}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
	Changing variables $h \mapsto X^{-1} h$, we get
	$$\Phi_{\chi}\left(g\right) = \frac{\chi\left(-1\right)^k}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(Xg\right)\right) \fieldCharacter\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter\left(-\trace X\right).$$
	Changing variables again $h \mapsto -h$ and setting $Xg = x$ and $-X = y$, we get  
	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
\end{proof}

We now use this to compute $\dblJacobiSum{\tau}{\chi}$. We have that $$\dblJacobiSum{\tau}{\chi} = \chi\left(-1\right)^k q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \tau\left(-y^{-1} x\right).$$
The last equality implies the following result.
\begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
	$$\dblJacobiSumScalar{\tau}{\chi} = \chi\left(-1\right)^k \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
\end{theorem}

@@

Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a character. As before, the assignment $\Phi_{\chi} \colon \GL_{\quadraticExtension}\left(\hermitianSpace\right) \to \cComplex$ given by $$\Phi_{\chi}\left(g\right) = \begin{dcases}
\chi\left(\detQuadratic\left( \idmap_{\hermitianSpace} - g\right)\right) & \text{if }\detQuadratic\left( \idmap_{\hermitianSpace} - g\right) \ne 0\\
0 & \text{otherwise,}
\end{dcases}$$
is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$.

Let $\pi$ be an irreducible representation of $H$ where $H \in \{G, \GroupExtension{G}\}$. Denote $$\dblJacobiSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \Phi_{\chi}\left(g\right).$$
Since $\Phi_{\chi}$ is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$, it is also a class function of $G$. Since $G$ is a normal subgroup of $H$, we have that $\dblJacobiSum{\pi}{\chi} \in \Hom_{H}\left(\pi, \pi\right)$. By Schur's lemma, there exists a constant $\dblJacobiSumScalar{\pi}{\fieldCharacter} \in \cComplex$, such that $$\dblJacobiSum{\pi}{\chi} = \dblJacobiSumScalar{\pi}{\chi} \cdot \idmap_\pi.$$
We call $\dblJacobiSumScalar{\pi}{\chi}$ the \emph{doubling method Jacobi sum}.

@@

\begin{theorem}\label{thm:multiplicativity-in-terms-of-gauss-sums}
	Let $\pi'$ be an irreducible representation of $H'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\quadraticExtension\right)$. Then for any irreducible representation $\pi$ of $H$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{H}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\involutionPlusOne{\chi} \ne 1$, we have
	$$\dblJacobiSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}^k \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter_{\quadraticExtension}} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter_{\quadraticExtension}} \dblJacobiSumScalar{\pi'}{\chi}.$$
\end{theorem}
\begin{proof}
	Let $v_{\pi'} \in \pi'$ and $v_{\tau} \in \tau$. Consider $f \in \rho$ defined as follows. The function $f \in \rho$ is the unique element supported on $P$, such that $f\left(\idmap_{\hermitianSpace}\right) = v_{\tau} \otimes v_{\pi'}$. The projection $f$ to any non-zero invariant subspace of $\rho$ is non-zero. We compute $\dblJacobiSum{\rho}{\chi} f$.

	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \Phi_{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \Phi_{\chi}\left(x^{-1} p\right),$$
	which can be rewritten as
	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
	As before, we may write
	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic \left(-h\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h\right)\right)\right).$$
	Hence, \begin{align*}
		\chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(Ah\right)\right) \\
		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	Assume that $\chi \ne 1$. By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$. Let us replace $h$ with $A^{-1} h$. We get the sum
	\begin{align*}
		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right) \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A x l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
	The inner sum over $N$ will vanish unless $Ax \in P$. Thus we have
	\begin{align*}
		\chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p - x^{-1} \in P$, which implies that $x \in P \cap G$.

>>>>

% Finite field macros
\newcommand{\FieldNorm}[2]{\mathrm{N}_{#1:#2}}
\newcommand{\aFieldNorm}{\mathrm{N}}
\newcommand{\finiteField}{\mathbb{F}}
\newcommand{\quadraticExtension}{\mathbb{E}}
\newcommand{\finiteFieldExtension}[1]{\finiteField_{#1}}
\newcommand{\quadraticFieldExtension}[1]{\quadraticExtension_{#1}}
\newcommand{\NormOneGroup}[1]{\finiteFieldExtension{#1}^{\aFieldNorm = 1}}
\newcommand{\algebraicClosure}[1]{\overline{#1}}
\newcommand{\Galois}{\operatorname{Gal}}
\newcommand{\Frobenius}{\operatorname{Fr}}
\newcommand{\restrictionOfScalars}[3]{\operatorname{Res}_{#1 \slash #2}{#3}}
\newcommand{\multiplcativeScheme}{\algebraicGroup{G}_m}
\newcommand{\affineLine}{\mathbb{A}^1}
\newcommand{\squareMatrix}{\operatorname{Mat}}
\newcommand{\Mat}[2]{\operatorname{Mat}_{#1 \times #2}}
\newcommand{\GaussSum}[2]{\mathcal{G}\left(#1, #2\right)}
\newcommand{\dblJacobiSum}[2]{\mathcal{J}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\posDblJacobiSum}[2]{\mathcal{J}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\negDblJacobiSum}[2]{\mathcal{J}_{-}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\JacobiKernel}[1]{\Phi_{#1}}
\newcommand{\posJacobiKernel}[1]{\Phi^{+}_{#1}}
\newcommand{\negJacobiKernel}[1]{\Phi^{-}_{#1}}
\newcommand{\genJacobiKernel}[1]{\Phi^{\pm}_{#1}}

\newcommand{\GaussSumScalar}[2]{\mathrm{G}\left(#1, #2\right)}
\newcommand{\dblJacobiSumScalar}[2]{\mathrm{J}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\posDblJacobiSumScalar}[2]{\mathrm{J}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\negDblJacobiSumScalar}[2]{\mathrm{J}_{-}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblVirtualJacobiSumScalar}[2]{\mathrm{j}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\posDblVirtualJacobiSumScalar}[2]{\mathrm{j}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblGammaFactor}[3]{\Gamma^{\mathrm{dbl}}\left(#1 \times #2, #3\right)}
\newcommand{\dblGammaFactorSpace}[4]{\Gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\dblLanglandsGammaFactorSpace}[4]{\gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\GaussSumCharacter}[3]{\tau\left(#1 \times #2, #3\right)}
\newcommand{\ladicnumbers}{\algebraicClosure{\mathbb{Q}_{\ell}}}
\newcommand{\IsometryGroup}{\mathrm{Isom}}
\newcommand{\lieAlgebra}{\mathfrak{g}}
\newcommand{\DeligneLusztigInduction}[2]{\mathrm{R}_{#1}^{#2}}
\newcommand{\algebraicGroup}[1]{\boldsymbol{\mathrm{#1}}}
\newcommand{\LusztigSeries}[2]{\mathcal{E}\left(#1, (#2)\right)}
\newcommand{\characteristicPolynomial}{\operatorname{CharPoly}}
\newcommand{\DualFrobeniusFixedPoints}[2][\Frobenius^{\ast}]{\algebraicGroup{#2}^{\ast #1}}
\newcommand{\FrobeniusFixedPoints}[2][\Frobenius]{\algebraicGroup{#2}^{#1}}
\newcommand{\CharacterLattice}[1]{X^{\ast}\left(#1\right)}
\newcommand{\CocharacterLattice}[1]{X_{\ast}\left(#1\right)}

@@

Consider the following assignment $\GL_k\left(\finiteField\right) \to \cComplex$
$$\Phi_{\chi}\left(g\right) = \begin{dcases}
	\chi\left(\det\left(\IdentityMatrix{k}+g\right)\right) & \text{if }\det\left(\IdentityMatrix{k}+g\right) \ne 0,\\
	0 & \text{otherwise.}
\end{dcases}$$
It is clear that $\Phi_{\chi}$ is a class function of $\GL_k\left(\finiteField\right)$.

Given an irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$, we consider the following \emph{doubling method Jacobi sum}:
$$\posDblJacobiSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{g \in \GL_k\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \tau\left(g\right).$$
Then $\posDblJacobiSum{\tau}{\chi}$ defines an element of $\Hom_{\GL_k\left(\finiteField\right)}\left(\tau, \tau\right)$. Therefore, by Schur's lemma there exists a complex number $\posDblJacobiSumScalar{\tau}{\chi} \in \cComplex$ such that $$\posDblJacobiSum{\tau}{\chi} = \posDblJacobiSumScalar{\tau}{\chi} \cdot \idmap_\tau.$$

The goal of this section is to express $\posDblJacobiSumScalar{\tau}{\chi}$ in terms of Kondo's Gauss sum.

\begin{proposition}\label{prop:doubling-for-gln-in-terms-of-kondo}
	We have the identity
	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
			y^{-1} x = g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
\end{proposition}
\begin{proof}
	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g+\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
	By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $X \in \GL_k\left(\finiteField\right)$. Thus	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g+\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
	Changing variables $h \mapsto X^{-1} h$, we get
	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(Xg\right)\right) \fieldCharacter\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter\left(\trace X\right).$$
	Changing variables again $h \mapsto -h$ and setting $Xg = x$ and $X = y$, we get  
	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
			y^{-1} x = g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
\end{proof}

We now use this to compute $\posDblJacobiSum{\tau}{\chi}$. We have that $$\posDblJacobiSum{\tau}{\chi} = q^{-k^2} \chi\left(-1\right)^k \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \tau\left(y^{-1} x\right).$$
The last equality implies the following result.
\begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
	$$\posDblJacobiSumScalar{\tau}{\chi} = \chi\left(-1\right)^k \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
\end{theorem}

We can define analogous sums $\negDblJacobiSum{\tau}{\chi}$ and $\negDblJacobiSumScalar{\tau}{\chi}$ by the formulas
$$\negDblJacobiSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{g \in \GL_k\left(\finiteField\right)} \Phi_{\chi}\left(-g\right) \tau\left(g\right) = \negDblJacobiSumScalar{\tau}{\chi} \cdot \idmap_{\tau}.$$
Then we have the simple relation
$$\negDblJacobiSumScalar{\tau}{\chi} = \centralCharacter{\tau}\left(-1\right) \posDblJacobiSumScalar{\tau}{\chi}.$$

@@

Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a character. As before, the assignment $\JacobiKernel{\chi} \colon \GL_{\quadraticExtension}\left(\hermitianSpace\right) \to \cComplex$ given by $$\JacobiKernel{\chi}\left(g\right) = \begin{dcases}
\chi\left(\detQuadratic\left( \idmap_{\hermitianSpace} + g\right)\right) & \text{if }\detQuadratic\left( \idmap_{\hermitianSpace} + g\right) \ne 0\\
0 & \text{otherwise,}
\end{dcases}$$
is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$. Denote for $g \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$, $\posJacobiKernel{\chi}\left(g\right) = \JacobiKernel{\chi}\left(g\right)$ and $\negJacobiKernel{\chi}\left(g\right) = \JacobiKernel{\chi}\left(-g\right)$.

Let $\pi$ be an irreducible representation of $H$ where $H \in \{G, \GroupExtension{G}\}$. Denote $$\dblJacobiSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \genJacobiKernel{\chi}\left(g\right).$$
Since $\genJacobiKernel{\chi}$ is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$, it is also a class function of $G$. Since $G$ is a normal subgroup of $H$, we have that $\dblJacobiSum{\pi}{\chi} \in \Hom_{H}\left(\pi, \pi\right)$. By Schur's lemma, there exists a constant $\dblJacobiSumScalar{\pi}{\fieldCharacter} \in \cComplex$, such that $$\dblJacobiSum{\pi}{\chi} = \dblJacobiSumScalar{\pi}{\chi} \cdot \idmap_\pi.$$
We call $\posDblJacobiSumScalar{\pi}{\chi}$ and $\negDblJacobiSumScalar{\pi}{\chi}$ the \emph{doubling method Jacobi sums}.

@@

\begin{theorem}\label{thm:multiplicativity-in-terms-of-gauss-sums}
	Let $\pi'$ be an irreducible representation of $H'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\quadraticExtension\right)$. Then for any irreducible representation $\pi$ of $H$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{H}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\involutionPlusOne{\chi} \ne 1$, we have
	$$\dblJacobiSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(\pm 1\right) \chi\left(\pm 1\right)^k \GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}^k \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter_{\quadraticExtension}} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter_{\quadraticExtension}} \dblJacobiSumScalar{\pi'}{\chi}.$$
\end{theorem}
\begin{proof}
	Let $v_{\pi'} \in \pi'$ and $v_{\tau} \in \tau$. Consider $f \in \rho$ defined as follows. The function $f \in \rho$ is the unique element supported on $P$, such that $f\left(\idmap_{\hermitianSpace}\right) = v_{\tau} \otimes v_{\pi'}$. The projection $f$ to any non-zero invariant subspace of $\rho$ is non-zero. We compute $\dblJacobiSum{\rho}{\chi} f$.

	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \genJacobiKernel{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \genJacobiKernel{\chi}\left(x^{-1} p\right),$$
	which can be rewritten as
	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \genJacobiKernel{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
	As before, we may write
	$$\genJacobiKernel{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm g - h \right)\right)\right).$$
	Hence, \begin{align*}
		q^{k^2} \sum_{p \in P} \genJacobiKernel{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(-Ah\right)\right) \\
		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm x^{-1} p\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	Assume that $\chi \ne 1$. By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$. Let us replace $h$ with $-A^{-1} h$. We get the sum
	\begin{align*}
		& \chi\left(-1\right)^k \sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right)\\
		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm x^{-1}p\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(\pm A x^{-1} l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
	The inner sum over $N$ will vanish unless $\pm Ax^{-1} \in P$ \elad{This is not true in general}. Thus we have
	\begin{align*}
		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left( p \mp x  \right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p \mp x \in P$, which implies that $x \in P \cap G$.
